Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} 
in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. After measuring the 
topography (SICM) the nanopipette could be moved to places - e.g. the z-grooves of the cell 
\cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} - where the adrenoceptor distribution 
should be investigated. Then the pipette could be used for stimulating the receptor to procuce 
cAMP oder cGMP \cite{Xiang2003}, this could bind to the FRET sensor, which changes 
its conformation and a FRET signal could be detected \cite{Nikolaev2010}.

>>>>

SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} 
in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. After measuring the 
topography (SICM) the nanopipette could be moved to places - e.g. the z-grooves of the cell 
\cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} - where the adrenoceptor distribution 
should be investigated. Then the pipette could be used for stimulating the receptor to procuce 
cAMP oder cGMP \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes 
its conformation and a FRET signal could be detected \cite{Nikolaev2010}.
